\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}

\setmainfont{Electra LT Std}
\newcommand{\infosep}{\hspace{2pt} | \hspace{2pt}}

\begin{document}
  {\centering
    {\LARGE \textbf{\textsc{Zachary G. Baylin}}}

    \vspace{3pt}

    me@zachbayl.in \infosep (770) 722-8911 \infosep 155 Spalding Creek Ct, Atlanta, GA 30350

  }
  \begin{flushright}
    September 23, 2019
  \end{flushright}

  \begin{flushleft}
    \noindent George P. Burdell\\
    White \& Gold\\
    801 Atlantic Drive\\
    Atlanta, GA 30332
  \end{flushleft}

  \noindent Dear Mr. Burdell,

  ~

  I am a first-year Computer Science student at the Georgia Institute of Technology, with interests in engineering software for quantitative financial applications. I am contacting you in regards to the Software Engineering position you have listed as available online. I learned of the position while browsing Angel, and was immediately intrigued by how your current team was able to develop proprietary trading algorithms and solve complex mathematical puzzles. I have worked on projects within this realm, such as SECurity-py, an application that helps traders analyze the trends of big financial firms by historically tracking the trends of their holdings, as released through 13F-HR forms. As such, I believe based both on my passion for the topic of quantitative finance, and my qualifications therein, I would be an excellent fit for this position at White \& Gold.

  ~

  Most recently, I have been serving as CTO and lead developer at an educational software company I founded: Rolltrax LLC. Through my ongoing experience with Rolltrax, I have realized that my passions lie much more in the abstract mathematical realm of software engineering. I have been lucky enough to take charge on many internal open-source projects that have helped me strengthen this passion. I also have developed an enthusiasm for algorithm development through taking Applied Combinatorics, a class taught by Dr. Tom Trotter at Georgia Tech.

  ~

  As a student at Georgia Tech, I either have taken, or will take, numerous classes that will build a solid foundation for the skills required for your position at White \& Gold. I am also enthusiastic about teaching myself principles of software engineering. I have been programming since I was only ten years-old, and even though I have had little formal computer science education up to this point, I have a breadth of knowledge in the field, whether it be from the projects I did on my own, or through my company Rolltrax.

  ~

  I am confident that my technical skills, interests, and prior experiences are an exemplary fit to the needs of not only position, but to White \& Gold as a whole. I am excited to see what interesting challenges this position might bring, and I hope to help provide continued success to your corporation. If you have any questions or concerns about my background, experience, or abilities to contribute to White \& Gold, you can contact me via email (me@zachbayl.in) or phone ((770) 722-8911). Thank you for your consideration, and I look forward to hearing back from you soon.

  ~

  \noindent Regards,\\
  Zachary G. Baylin

\end{document}