\documentclass{article}
\usepackage[margin=.5in]{geometry}
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xhfill}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\setlength\parindent{0pt}
\setmainfont[Scale=0.95,ItalicFont={Linguistics Pro Italic}]{Linguistics Pro}
\linespread{1.1}

\setlist[itemize]{nolistsep, topsep=0pt, leftmargin=12pt}

\pagenumbering{gobble}
\def\labelitemi{$\ast$}

\newcommand{\sectionHeader}[1]{{\large \textbf{#1}}\hspace{5pt}\xrfill[.6ex]{.4pt}}

\newcommand{\headerInfoSpacer}{\hspace{10pt}}

\newcommand{\sectionSpacer}{\vspace{6pt}}

\begin{document}
  \begin{center}
    \textbf{{\Huge Zachary G. Baylin}}

    \vspace{3pt}

    \href{mailto:me@zachbayl.in}{\faEnvelope \hspace{1pt} me@zachbayl.in} \headerInfoSpacer \faPhone \hspace{1pt} (770) 722-8911 \headerInfoSpacer \faIcon{map-marker-alt} Atlanta, GA \headerInfoSpacer \href{https://linkedin.com/in/zbaylin}{\faLinkedin \hspace{1pt} zbaylin} \headerInfoSpacer \href{https://github.com/zbaylin}{\faGithub \hspace{1pt} zbaylin} \headerInfoSpacer \href{https://zachbayl.in}{\faGlobeAmericas \hspace{1pt} zachbayl.in}\\
  \end{center}

  \sectionHeader{Personal Statement}

  \vspace{3pt}

  Analytical and intellectually curious developer with a passion for mathematical problem-solving through programming.

  \sectionSpacer

  \sectionHeader{Education}

  \vspace{3pt}

  \textbf{Georgia Institute of Technology} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} Atlanta, GA \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} Expected Graduation Summer 2022\\
  Candidate for B.S. in Computer Science\\
  Concentrating in System Architecture \& Theory\\
  Major GPA: 4.0, Cumulative GPA: 4.0

  \sectionSpacer

  \sectionHeader{Work Experience}

  \href{https://www.skolem.tech/}{\textbf{Skolem Labs}} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} Remote (Chicago, IL) \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} June 2021 - Present\\
  {\footnotesize \faIcon{briefcase}} \hspace{1pt} \textit{Consultant, Part-time Software Engineer}
  \begin{itemize}
    \item Developing software in OCaml to support a decentralized finance (DeFi) trading platform
  \end{itemize}

  \vspace{3pt}

  \href{https://www.goldmansachs.com/}{\textbf{Goldman Sachs}} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} New York, NY \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} June 2021 - August 2021\\
  {\footnotesize \faIcon{briefcase}} \hspace{1pt} \textit{Intern, Investment Banking Engineering}
  \begin{itemize}
    \item Helped develop \href{https://www.bloomberg.com/news/articles/2017-06-13/goldman-set-out-to-automate-ipos-and-it-s-come-far-really-fast}{Deal Link}, a platform used by bankers to automate commercial lending processes.
    \item Increased financial data quality in response to federal regulations using a custom language-agnostic rules engine.
    \item Interacted with bankers and quantitative strategists to understand and develop dynamic rules to fit changing business needs.
    \item Interfaced with both internal and external APIs to build a cohesive model of lending information.
  \end{itemize}

  \vspace{3pt}

  \href{https://www.facebook.com/}{\textbf{Facebook}} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} Remote (Seattle, WA) \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} January 2021 - April 2021\\
  {\footnotesize \faIcon{briefcase}} \hspace{1pt} \textit{Software Engineer Intern} 
  \begin{itemize}
    \item Developed solutions for advertisers to help better target their advertisements while maintaining user privacy.
    \item Automated the provisioning of SSL certificates on ad-hoc AWS EC2 instances for Facebook clients.
    \item Helped transition software from a standalone model to a clustered approach using Docker, Kubernetes, \& Kong.
    \item Coordinated the release of a new version of software used by clients while maintaining compatibility with Facebook APIs.
  \end{itemize}

  \vspace{3pt}

  \href{https://www.outrunlabs.com/}{\textbf{Outrun Labs LLC}} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} Remote (Seattle, WA) \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} May 2020 - August 2020\\
  {\footnotesize \faIcon{briefcase}} \hspace{1pt} \textit{Software Engineer Intern} 
  \begin{itemize}
    \item Helped to develop the \href{https://github.com/revery-ui/revery}{Revery} cross-platform GUI framework by implementing key features and deepening integration into supported platforms.
    \item Worked on \href{https://onivim.io/}{Onivim}, a modal text editor based on vim, implementing features such as hover, signature help, and font fallback in ReasonML/OCaml.
    \item Integrated with system APIs in C/C++ (Win32 \& GTK3) \& Objective-C (Cocoa) using the OCaml foreign function interface.
  \end{itemize}

  \href{https://rolltrax.com}{\textbf{Rolltrax LLC}} \hspace{3pt} {\footnotesize \faIcon{map-marker-alt}} Atlanta, GA \hspace*{\fill} {\footnotesize \faIcon{calendar}} \hspace{1pt} August 2017 - August 2019\\
  {\footnotesize \faIcon{briefcase}} \hspace{1pt} \textit{Co-Founder \& Software Engineer}
  \begin{itemize}
    \item Developed a full-stack SaaS solution for work-based learning coordinators and students to take attendance and manage their work. The system is composed of a Crystal web API and a ReasonReact frontend.
    \item Beta tested the system at North Springs High School over two years in order to determine the needs of our clients.
  \end{itemize}

  \sectionSpacer

  \sectionHeader{Projects}

  \vspace{3pt}

  \begin{itemize}
    \item \textbf{xv6 Operating System}: Improved upon the UNIX-based educational operating system by implementing the following features: copy-on-write forking, lazy page allocation, priority-based scheduling, user-space threading, filesystem permissions, et. al.
    \item \href{https://github.com/revery-ui/revery}{\textbf{Revery}}: Contributed to the Revery cross-platform GUI framework, which enables developers to build consistent user interfaces across multiple platforms. Implemented various key features such as font-fallback and font families, and deepened native integration through platform specific APIs.
    \item \href{https://github.com/zbaylin/ReQuests}{\textbf{ReQuests}}: Created a web requests library in ReasonML/OCaml using cURL that supports parallelism through libuv.
  \end{itemize}

  \sectionSpacer

  \sectionHeader{Skills}
  \begin{itemize}
    \item \textbf{Languages/Tools}: OCaml, ReasonML, C, Java, Ruby, Kotlin, Crystal, Objective-C, Cocoa, SQL, TypeScript, Win32, Cocoa
    \item \textbf{Relevant Coursework}: Systems \& Networks, Operating Systems, Applied Combinatorics, Number Theory \& Cryptography, Abstract Linear Algebra, Compilers and Interpreters, Graduate Algorithms, High Performance Computer Architecture 
  \end{itemize}

\end{document}
